\documentclass[12pt]{article}

\usepackage{fullpage}
\usepackage{amsmath,amsfonts}
\usepackage{textgreek}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Minion Pro}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

%% Fixes for letterspacing that work with XeLaTeX
\newcommand{\allcapsspacing}[1]{{\addfontfeature{LetterSpace=7.5}#1}}
\newcommand{\smallcapsspacing}[1]{{\addfontfeature{LetterSpace=5.0}#1}}
\renewcommand{\textsc}[1]{\smallcapsspacing{\scshape{#1}}}

\usepackage{CV}

\newcommand{\tworowstwocolsitem}[4]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
		#3 & #4 \\
\end{tabular*}\vspace{0.75\baselineskip}}

\newcommand{\educationitem}[4]{
\tworowstwocolsitem{#1}{#2}{\textit{#3}}{\textit{#4}}}

\newcommand{\teachingitem}[4]{
\tworowstwocolsitem{#1}{#2}{\textit{#3}}{#4}}

\newcommand{\leadershipitem}[3]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
\end{tabular*}\newline#3\vspace{0.75\baselineskip}\par}

\newcommand{\outreachitem}[4]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
		#3 & \\
\end{tabular*}\newline#4\vspace{0.75\baselineskip}\par}

\newcommand{\researchitem}[4]{
\outreachitem{#1}{#2}{\textit{#3}}{Topic: #4}}

\newcommand{\yearitem}[2]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
\end{tabular*}\vspace{0.75\baselineskip}}

\usepackage{titlesec}
\titleformat{\section}{}{}{}{\hrule\vspace{0.5\baselineskip}\sffamily\Large\uppercase}{}{}
\titlespacing{\section}{0pt}{-15pt}{*1}

% enables reverse numbering
\usepackage[leftmargin=12pt, itemsep=0.5\baselineskip]{etaremune}

\begin{document}

%\Header
\begin{center}
\Large{\sffamily\allcapsspacing{\uppercase{Rebecca Faye Alford}}}

\normalsize{\textsc{Carnegie Mellon University, SMC 2858 \\
5000 Forbes Ave, Pittsburgh, PA 15289 \\
\vspace{0.25\baselineskip}
ralford@andrew.cmu.edu}}
\end{center}

%\Education
\section*{\allcapsspacing{Education}}
\educationitem{Carnegie Mellon University}{Pittsburgh, PA}{B.S. Chemistry, Concentration: Computational Chemistry}{May 2016}
\educationitem{The Johns Hopkins University}{Baltimore, MD}{Visiting Undergraduate - Chemical \& Biomolecular Engineering}{May 2013--Present}

%\Research Experience
\section*{\allcapsspacing{Research Experience}}
\researchitem{NIH Undergraduate Research Fellow, The Johns Hopkins University}{2013--Present}{Advisor: Dr. Jeffrey J. Gray}{Computational modeling of membrane proteins}
\researchitem{Software Engineering Intern, Spatial4j}{Spring 2014}{Advisor: David Smiley}{Modeling of geodesic shapes in object-oriented Spatial4j}
\researchitem{High School Research Assistant, New York University}{2011--2013}{Advisors: Dr. Richard Bonneau}{Prediction of deleterious protein variants using structure prediction}
\researchitem{High School Research Assistant, Stony Brook University}{2009--2010}{Advisor: Dr. Maurice Kernan}{Characterization of TRPM ion channel function in Drosophila}

\section*{\allcapsspacing{Publications}}
\begin{etaremune}
\item Baugh EH, Simmons-Elder R, Muller C, \textbf{Alford RF}, Volovsky N, Lash A, Bonneau R (2015) ``Structural modeling improves classification and interpretation of deleterious protein variation,'' \textit{Under Review}
\item \textbf{Alford RF*}, Koehler Leman J*, Weitzner BD, Duran AM, Tilley DC, Elazar A, Gray JJ (2015) ``An integrated framework for computational modeling and design of membrane proteins,'' \textit{PLoS Comput. Biol.} In press. (* equal contribution authors)
\item Pope WH, Bowman CA, Russell DA, Jacobs-Sera D, Asai DJ, Cresawn SG, Jacobs WR, Hendrix RW, Lawrence JG, Hartfull GF, \textbf{SEA-PHAGES}, PHIRE (2015) ``Whole genome comparison of a large collection of mycobacteriophages reveals a continuum of phage genetic diversity variation'' \textit{eLife}, 4, 1-65. \textit{*Full author listing in manuscript. Contribution -- Isolated and characterized a novel phage computationally and experimentally}
\end{etaremune}

% some items use leadership item instead of year item to make the year appear in line with the top line for multiline entries
\section*{\allcapsspacing{Selected Honors and Awards}}
\yearitem{NIH Undergraduate Research Fellowship}{2013--Present}
\yearitem{Dean's List High Honors}{Fall 2014, Spring 2014, Spring 2015}
\yearitem{Mellon College of Science -- Ruth Welch Walker Scholarship}{2013--Present}
\yearitem{Grace Hopper Celebration of Women in Computing - Scholar}{2014}
\yearitem{Selected Student Speaker - TEDxCMU}{2013}
\yearitem{Best in Biochemistry - Intel International Science and Engineering Fair}{2012}
\yearitem{National Semifinalist - Intel Science Talent Search}{2012}
\yearitem{NASA Max Carpenter Award for Promise in Science and Engineering}{2010}

\section*{\allcapsspacing{Scientific Talks}}
\begin{etaremune}
\item Alford RF, Baugh EH, Gray JJ (2014) ``Real-time visualization of Rosetta membrane simulations using the PyMOL viewer'' \textit{Rosetta Developer's Meeting}, Seattle, WA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``RosettaMP - An object-oriented framework for modeling and design of membrane proteins in Rosetta'' \textit{Rosetta Developer's Meeting}, San Francisco, CA
\item Alford RF (2013) ``The Dream Machine'' \textit{TEDxCMU}, Pittsburgh, PA.
\end{etaremune}

\section*{\allcapsspacing{Scientific Posters}}
\begin{etaremune}
\item Alford RF, Fleming P, Fleming KG, Gray JJ (2015) ``Toward an all-atom energy function for scoring in membrane environments of diverse lipid composition'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Alford RF, Koehler Leman J, Gray JJ (2015) ``Validation of an intrinsic lipid bilayer model in the RosettaMP framework'' \textit{Gordon Research Conference -- Membrane Protein Folding}, Waltham, MA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``An integrated framework advancing membrane protein modeling and design'' \textit{Carnegie Mellon Meeting of the Minds Symposium}, Pittsburgh, PA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``A new object-orieented framework for modeling and design of membrane proteins in Rosetta'' \textit{Grace Hopper Conference for Women in Computing}, Phoenix, AZ.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``A new object-orieented framework for modeling and design of membrane proteins in Rosetta'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``A new object-orieented framework for modeling and design of membrane proteins in Rosetta'' \textit{Carnegie Mellon Meeting of the Minds Symposium}, Pittsburgh, PA.
\item Alford RF, Koehler Leman J, Gray JJ (2013) ``Redesigning the framework for membrane protein modeling in Rosetta'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Alford RF, Simmons-Elder R, Poultney C, Halvorsen L, Bonneau R (2012) ``A machine-learning based approach to predicting functional effects of mutations in membrane proteins'' \textit{Rosetta Conference}, Leavenworth, WA.
\end{etaremune}

\section*{\allcapsspacing{Teaching Experience}} %\ who are the students?!
\teachingitem{Co-Instructor, Rosetta REU Boot Camp}{Spring 2015}{A course on developing in Rosetta for undergraduate students} {Chapel Hill, NC}
\teachingitem{Co-Instructor, Rosetta Boot Camp}{Spring 2014}{A course on developing in Rosetta for graduate students and postdocs}{Chapel Hill, NC}
\teachingitem{Co-Developer and Co-Instructor, ThinkTech}{Fall 2014--Present}{A computational thinking course for middle school girls}{Pittsburgh, PA}

\section*{\allcapsspacing{Scientific Leadership}}
\leadershipitem{Assistant Organizer, Rosetta REU Program}{2015}{First REU supported by a virtual community. Assisted with admissions and adjusted boot camp materials for the undergraduate level}
\leadershipitem{High school research mentor}{2011--Present}{Mentor to six high school student researchers interested in computational structural biology and bioinformatics}
\leadershipitem{Organizer, Rosetta @ Grace Hopper}{Fall 2014}{Attended Grace Hopper for first time as Rosetta Organization. Created career fair materials, poster, and served as contact point for conference logisitcs}

\section*{\allcapsspacing{Activities and Outreach}}
\leadershipitem{Instructor and Volunteer, CMU Creative Technology Nights}{2013--Present}{Weekly 2hr workshops for middle school girls designed to increase STEM exposure}
\leadershipitem{Science Fair Judge, Plainview Old Bethpage Middle School}{2014, 2015}{Evaluated projects for annual 6th grade science fair}
\yearitem{Committee Member, Carnegie Mellon Women in Computer Science}{2014--Present}
\yearitem{Writer and Science Policy Director, The Triple Helix Undergraduate Journal}{2013--2015}
\leadershipitem{Team Captain, VisionWalk}{2012, 2013}{Organized teams in Long Island, NY and Pittsburgh, PA for annual walk to raise awareness for retinal disease}

\end{document}
