%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% Rebecca Alford's Short Form CV %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

%%% Preamble
\usepackage[margin=0.4in]{geometry}
\usepackage{textgreek}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Palatino}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Avenir Next}

%% Fixes for letterspacing that work with XeLaTeX
\newcommand{\allcapsspacing}[1]{{\addfontfeature{LetterSpace=7.5}#1}}
\newcommand{\smallcapsspacing}[1]{{\addfontfeature{LetterSpace=5.0}#1}}
\renewcommand{\textsc}[1]{\smallcapsspacing{\scshape{#1}}}

\usepackage{CV}

\newcommand{\tworowstwocolsitem}[4]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
		#3 & #4 \\
\end{tabular*}\vspace{0.5\baselineskip}}

\newcommand{\educationitem}[4]{
\tworowstwocolsitem{#1}{#2}{\textit{#3}}{#4}}

\newcommand{\teachingitem}[4]{
\tworowstwocolsitem{#1}{#2}{\textit{#3}}{#4}}

\newcommand{\leadershipitem}[3]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
\end{tabular*}\newline#3\vspace{0.5\baselineskip}\par}

\newcommand{\outreachitem}[4]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
		#3 & \\
\end{tabular*}\newline#4\vspace{0.5\baselineskip}\par}

\newcommand{\researchitem}[4]{
\outreachitem{#1}{#2}{\textit{#3}}{Topic: #4}}

\newcommand{\yearitem}[2]{
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		#1 & #2 \\
\end{tabular*}\vspace{0.5\baselineskip}}

\usepackage{titlesec}
\titleformat{\section}{}{}{}{\hrule\vspace{0.5\baselineskip}\sffamily\large\uppercase}{}{}
\titlespacing{\section}{0pt}{-18pt}{*1}

% enables reverse numbering
\usepackage[leftmargin=11pt, itemsep=0.15\baselineskip]{etaremune}

\pagestyle{empty}
\begin{document}

\begin{center}
\large{\sffamily\allcapsspacing{\uppercase{Rebecca F. Alford}}}

\normalsize{\textsc{Carnegie Mellon University, SMC 2858,
5000 Forbes Ave, Pittsburgh, PA 15289  \\
ralford@andrew.cmu.edu}}
\end{center}

%%% Section: Education
\section*{\allcapsspacing{Education}}

\educationitem{\textsc{Carnegie Mellon University}}{Pittsburgh, PA}{B.S. Chemistry, Concentration: Computational Chemistry}{Expected May 2016}
 
%%% Section: Research Experience
\section*{\allcapsspacing{Research Experience}}

\researchitem{Undergraduate Research Assistant, The Johns Hopkins University}{2013--Present}{Advisor: Dr. Jeffrey J. Gray}{Topic: \textit{Computational modeling of membrane proteins}}

\researchitem{High School Research Assistant, New York University}{2011--2013}{Advisor: Dr. Richard Bonneau}{Topic: \textit{Prediction of deleterious protein variants using structure prediction}}

\researchitem{High School Research Assistant, Stony Brook University}{2009--2010}{Advisor: Dr. Maurice Kernan}{Topic: \textit{Characterization of TRPM ion channel function in Drosophila}}

%%% Section: Publications
\section*{\allcapsspacing{Publications}}

\begin{etaremune}
\item Baugh EH, Simmons-Elder R, Muller CL, \textbf{Alford RF}, Volovsky N, Lash A, Bonneau R (2016) ``Robust classification of protein variation using structural modeling and large-scale data integration,'' \textit{Nucleic Acids Research} 44(6): 2501-2513.

\item \textbf{Alford RF*}, Koehler Leman J*, Weitzner BD, Duran AM, Tilley DC, Elazar A, Gray JJ (2015) ``An integrated framework advancing membrane protein modeling and design,'' \textit{PLoS Computational Biology} 11(9): e1004398 (*equal contribution authors).

\item Pope WH, Bowman CA, Russell DA, Jacobs-Sera D, Asai DJ, Cresawn SG, Jacobs WR, Hendrix RW, Lawrence JG, Hartfull GF, \textbf{SEA-PHAGES*}, PHIRE (2015) ``Whole genome comparison of a large collection of mycobacteriophages reveals a continuum of phage genetic diversity variation'' \textit{eLife}, 4, 1-65 (\textit{*Group Authorship - Full listing in manuscript}).
\end{etaremune}

%%% Section: Selected honors and awards
\section*{\allcapsspacing{Selected Honors and Awards}}

\yearitem{Hertz Foundation Fellowship}{2016}
\yearitem{National Science Foundation Fellowship}{2016}
\yearitem{Dr. J. Paul Pugassi and Linda Monteverde Award}{2016}
\yearitem{Carnegie Mellon Women's Association Award}{2016}
\yearitem{Handlos Research Award}{2016}
\yearitem{Senior Leadership Recognition Award}{2016}
\yearitem{Ruth Welch Walker Scholarship}{2012--2016}
\yearitem{Grace Hopper Conference Scholarship}{2014}
\yearitem{Selected Student Speaker--TEDxCMU}{2013}
\yearitem{Davidson Fellowship Honorable Mention}{2012}
\yearitem{Intel International Science and Engineering Fair--Best Biochemistry Project}{2012}
\yearitem{Intel Science Talent Search Semifinalist}{2012}
\yearitem{Max Carpenter Award for Promise in Science and Engineering}{2010}


%%% Section: Scientific talks
\section*{\allcapsspacing{Scientific Talks}}

\begin{etaremune}
\item \textbf{Alford RF} \textbf{Invited Keynote:} ``Decoding Biology -- Using computers to understand disease'' \textit{Winter Rosetta Conference}, Burlington, VT.
\item \textbf{Alford RF}, \textbf{Baugh EH}, Gray JJ (2014) ``Real-time visualization of Rosetta membrane simulations using the PyMOL viewer'' \textit{Rosetta Developer's Meeting}, Seattle, WA.
\item \textbf{Alford RF}, Koehler Leman J, Gray JJ (2014) ``RosettaMP - An object-oriented framework for modeling and design of membrane proteins in Rosetta'' \textit{Rosetta Developer's Meeting}, San Francisco, CA.
\item \textbf{Alford RF} (2013) ``The Dream Machine'' \textit{TEDxCMU}, Pittsburgh, PA.
\end{etaremune}

%%% Section: Scientific Posters
\section*{\allcapsspacing{Scientific Posters}}

\begin{etaremune}
\item Alford RF, Fleming P, Fleming KG, Gray JJ (2015) ``Toward an all-atom energy function for membrane protein modeling in bilayers of different lipid composition'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Alford RF, Fleming KG, Gray JJ (2015) ``Validation of the implicit membrane model in RosettaMP'' \textit{Gordon Research Conference -- Membrane Protein Folding}, Waltham, MA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``An integrated framework advancing membrane protein modeling and design'' \textit{Carnegie Mellon Meeting of the Minds Symposium}, Pittsburgh, PA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``A new object-orieented framework for modeling and design of membrane proteins in Rosetta'' \textit{Grace Hopper Conference for Women in Computing}, Phoenix, AZ.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``A new object-orieented framework for modeling and design of membrane proteins in Rosetta'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Alford RF, Koehler Leman J, Weitzner BD, Gray JJ (2014) ``Redesigning the framework for membrane protein modeling in Rosetta'' \textit{Carnegie Mellon Meeting of the Minds Symposium}, Pittsburgh, PA.
\item Alford RF, Koehler Leman J, Gray JJ (2013) ``Redesigning the framework for membrane protein modeling in Rosetta'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Alford RF, Simmons-Elder R, Poultney C, Halvorsen L, Bonneau R (2012) ``A machine-learning based approach to predicting functional effects of mutations in membrane proteins'' \textit{Rosetta Conference}, Leavenworth, WA.
\end{etaremune}

%%% Section: Teaching Experience
\section*{\allcapsspacing{Teaching and Mentoring Experience}}

\yearitem{Mentor to seven high school research students}{2011--Present}
\yearitem{Co-Instructor, Rosetta Intern Boot Camp}{May 2015}
\yearitem{Co-Instructor, Rosetta Boot Camp}{June 2014}
\yearitem{Co-Developer and Co-Instructor, ThinkTech}{2014--Present}

%%% Section: Science Outreach
\section*{\allcapsspacing{Activities and Science Outreach}}
\yearitem{Assistant Organizer, Rosetta REU Program}{2015}
\yearitem{Organizer, Rosetta Team at Grace Hopper}{2014}
\yearitem{Science Fair Judge, Plainview Old Bethpage Middle School}{2014, 2015}
\yearitem{Committee Member, Carnegie Mellon Women in Computer Science}{2014--Present}
\yearitem{Instructor and Volunteer, Carnegie Mellon Creative Technology Nights}{2013--Present}
\yearitem{Team Captain, VisionWalk}{2012, 2013}




\end{document}
